\fontsize{14}{14}Bachelor Thesis \\ in \\Allgemeine Informatik \fontsize{22}{22}\textbf{Transhumanism}\\ \fontsize{18}{18} The New Human

### 2014-01-13 draft.tex
SOme more changes

	      In the field of Transhumanism the idea of Bioengineering is a very important Topic. As humans we are limited by our own Body. We only have one and cannot replace it. This means we have to take care of it and try to fix any problems that arise. 

@@

        The past thousands of years if someone lost their legs they would be in a very difficult position. They would have to help their families to survive by being as productive as they ever have been. Obviously this was not always possible and thus that person would have been condemned to a life of misery.

@@

        Today with the help of prosthetics, almost anyone can keep living an almost normal life by wearing artifical legs. This however is still limited though. You wouldn't be able to move them as you would have moved your old legs. You don't feel through them either. This solution is not ideal either.

@@

        This brings us to the next Idea that many Transhumanists hold. \emph{Why just replace?} After all, if we are able to bridge the body-electronics problem, the only limit to our physical bodies would be our own knowledge and imagination. At this point a similar explosion of diversity might occur as it has happened to electronics. That is, many different Limb Modifications could appear on a sort of global market, bringing you features you did not posses before hand. Even if it sounds like science fiction, but the ability to handle cooking food with your, now bionic, hands might not be far off. And why not cook it directly through your hands? 

@@

        As the final advancement, the ability to replace the whole body would allow for a complete revolution of the human status. If we were able to exit our own bodies and evolve without them we could target our own evolution towards a specific goal.\cite{NBICReport} 

@@

        A more down to earth train of thought would be to think of the ways we could more easily monitor our own bodies. Diabetic patients would be able to lead a normal life with a special pump that is able to take readings much like a normal person's Pancreas would do. Once our understanding is far enough we might even replace the sick Pancreas completely.

@@

        But we would not have to stop at our own bodies and also monitor our environments. So workers that have to work in hazardous environments could have integrated Geiger Counters in their Eyes, allowing them to view disintegrations in real time. An Infrared sensor would also help many professionals as faulty equipment can show signs of overheating thus allowing preemptive reparations before any major accidents.

@@

	      If someone were to ask you today to multiply two by two, you will obviously give the answer of four. For simple mathematical questions we know the answer almost instantly. Problems usually start once we try to think about higher math problems. What is the answer to $4^4$? The answer is not instantly available to us. The past thousands of years we did not need to solve these types of problems to survive so our brains never had to adapt to it.

@@

	      Once we understand how the human brain functions we could draft extensions or replacements of the responsible parts and thus enhance our capabilities of difficult computation. This would be enough in a first moment, but once we realize that it might be possible to completely simulate a human brain we could survive without our bodies.\cite{FutureMinds}

@@

	This realization is core to the Transhumanist. Since transcending the Human body is one of the goals most aspire to. This has several implications in and of it self as well. Those familiar with Physolophical concepts about the human existence know that there are many currents of thought. 

>>>>

	      In the field of Transhumanism the idea of Bioengineering is a very important Topic. 
        As humans we are limited by our own Body. 
        We only have one and cannot replace it. 
        This means we have to take care of it and try to fix any problems that arise. 

@@

        The past thousands of years if someone lost their legs they would be in a very difficult position. 
        They would have to help their families to survive by being as productive as they ever have been. 
        Obviously this was not always possible and thus that person would have been condemned to a life of misery.

@@

        Today with the help of prosthetics, almost anyone can keep living an almost normal life by wearing artifical legs. 
        This however is still limited though. 
        You wouldn't be able to move them as you would have moved your old legs. 
        You don't feel through them either. 
        This solution is not ideal either.

@@

        This brings us to the next Idea that many Transhumanists hold. \emph{Why just replace?} 
        After all, if we are able to bridge the body-electronics problem, the only limit to our physical bodies would be our own knowledge and imagination. 
        At this point a similar explosion of diversity might occur as it has happened to electronics. 
        That is, many different Limb Modifications could appear on a sort of global market, bringing you features you did not posses before hand. 
        Even if it sounds like science fiction, but the ability to handle cooking food with your, now bionic, hands might not be far off. 
        And why not cook it directly through your hands? Or get by with solid food all the way?

@@

        As the final advancement, the ability to replace the whole body would allow for a complete revolution of the human status. 
        If we were able to exit our own bodies and evolve without them we could target our own evolution towards a specific goal.\cite{NBICReport} 

@@

        A more down to earth train of thought would be to think of the ways we could more easily monitor our own bodies. 
        Diabetic patients would be able to lead a normal life with a special pump that is able to take readings much like a normal person's Pancreas would do. 
        Once our understanding is far enough we might even replace the sick Pancreas completely.

@@

        But we would not have to stop at our own bodies and also monitor our environments. 
        So workers that have to work in hazardous environments could have integrated Geiger Counters in their Eyes, allowing them to view disintegrations in real time. 
        An Infrared sensor would also help many professionals as faulty equipment can show signs of overheating thus allowing preemptive reparations before any major accidents.

@@

	      If someone were to ask you today to multiply two by two, you will obviously give the answer of four. 
        For simple mathematical questions we know the answer almost instantly. Problems usually start once we try to think about higher math problems. 
        What is the answer to $4^4$? The answer is not instantly available to us. 
        The past thousands of years we did not need to solve these types of problems to survive so our brains never had to adapt to it.

@@

	      Once we understand how the human brain functions we could draft extensions or replacements of the responsible parts and thus enhance our capabilities of difficult computation. 
        This would be enough in a first moment, but once we realize that it might be possible to completely simulate a human brain we could survive without our bodies.\cite{FutureMinds}

@@

        This realization is core to the Transhumanist. 
        Since transcending the Human body is one of the goals most aspire to. 
        This has several implications in and of it self as well. 
        Those familiar with Physolophical concepts about the human existence know that there are many currents of thought. 
